% ;; -*- coding: iso-latin-1; TeX-PDF-mode: t; TeX-master: "main" -*-%

\documentclass{article}
\usepackage{xspace}
\usepackage{epsfig}
\usepackage{latexsym,amssymb,stmaryrd}
\usepackage{fancybox,epic}
\usepackage[algoruled,vlined,english]{algorithm2e}
\usepackage{amsmath}
\usepackage{colortbl}
\usepackage{caption}
\usepackage{color} 
\usepackage{graphics}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage[draft]{fixme}
\usepackage[color=green!20]{todonotes}
\usepackage{tikz}
\usepackage{wrapfig}
\usepackage{multicol}
\usepackage{paralist}

\usepackage{arydshln}

\usepackage{url}

\usepackage{listings}
\lstset{ 
  frame=Ltb,
  framerule=0pt,
  aboveskip=0mm,
  framextopmargin=10pt,
  framexbottommargin=0pt,
  framexleftmargin=0cm,
  framesep=0pt,
  rulesep=0pt,
  % 
  stringstyle=\ttfamily,
  showstringspaces = false,
  basicstyle=\small\sffamily,
  commentstyle=\color{black},
  keywordstyle=\small\bfseries,
  % 
  numbers=left,
  mathescape=true,
  numbersep=-5pt,
  numberstyle=\tiny,
  numberfirstline=true,
  numberblanklines=true,
  firstnumber=auto,
  breaklines=true,
  language=Java,
  morekeywords={if,then,else,while,do,return,await,get,skip,release,begin} 
}



\begin{document}



\title{EasyPeople: Manage Large DB of people.}


\author{Jes\'us Dom\'enech}

\maketitle 

\section{Requirements}

\subsection{CSV to CSV-normal}

\subsubsection{Explanation}
Given a CSV of People Get a new CSV with:
\begin{itemize}
\item Extend names.
\item ``DNI'' like 00000000N
\item normalize dates.
\item normalize Custom-Fields.
\item Select From list.
\end{itemize}

\subsubsection{Recepie}
To solve this we do the following steps:
\begin{enumerate}
\item Read CSV by columns.
\item Apply to each column a normalizer. (Prevent whites and don't
  reorder anything)
\item Write CSV-normal row-by-row, with reordered columns and empty info.
\end{enumerate}

\subsubsection{Modules: Low Level}
\begin{itemize}
\item CSV Handler
\begin{itemize}
\item ReadCSV : filepath $\Rightarrow$  Array[people][info]
\item WriteNormalCSV : Array[people][multi-info] filepath $\Rightarrow$ bool
\end{itemize}
\item Normalizer
\begin{itemize}
\item Normalize : Array[columnName, info-people] $\Rightarrow$  Array[columnName,[info]]
\item NormalizeDate : string $\Rightarrow$ Normal-Date-string
\item NormalizePhone: string $\Rightarrow$ [number]
\item NormalizeName : string $\Rightarrow$ Normal-Name-string
\item NormalizeListItem : string List $\Rightarrow$ Normal-string
\item NormalizeDNI  : string $\Rightarrow$ Normal-DNI-string
\item toNumber      : string $\Rightarrow$ number
\end{itemize}
\end{itemize}

\subsection{Find Duplicates}

\subsection{CSV to Excel}

\subsection{Filter Excel}

\end{document}
